---
title: "Observed2M_Model"
author: "Ben Weinstein"
date: "June 6, 2016"
output: html_document
---

```{r,warning=FALSE,message=FALSE,echo=FALSE,cache=FALSE}
library(reshape2)
library(chron)
library(ggplot2)
library(knitr)
library(R2jags)
library(dplyr)
library(stringr)
library(gridExtra)
library(boot)
library(bipartite)
library(lme4)
opts_chunk$set(message=FALSE,warning=FALSE,fig.width=10,fig.height=7,echo=TRUE,cache=F,fig.align='center',fig.path="figureObserved/")

#new model update
newModel<-T
```

```{r,echo=F,cache=FALSE}
paste("Run Completed at",Sys.time())
```

```{r,eval=T}
#Load in data from Observed2m_Generate.Rmd
load("Observed.RData")
#load("ObservedModel.RData")
newModel<-T
```

```{r}
#source functions
source("Bayesian/BayesFunctions.R")
```

#View Raw Data
```{r}
ggplot(indat,aes(x=Traitmatch,y=Yobs,col=as.factor(R))) + facet_wrap(~Hummingbird,ncol=4,scales="free") + geom_point() + geom_smooth(method = "glm",method.args=list(family="poisson")) + scale_color_manual("Resource Availability",values=c("black",'blue','red'))

ggplot(indat[indat$Yobs==1,],aes(x=Traitmatch,fill=as.factor(R))) + facet_wrap(~Hummingbird,ncol=4,scales="free") + geom_density(alpha=.7) + scale_fill_manual("Resource Availability",values=c("black",'blue','red'))

m<-glmer(data=indat[,],Yobs~Traitmatch*R+(1|Hummingbird),family="poisson")
summary(m)
indat$pred<-predict(m,type="response")
ggplot(indat,aes(x=Traitmatch)) + geom_point(aes(y=Yobs)) + geom_line(aes(y=pred,col=as.factor(R)))
```

#Hierarchical Occupancy Model

For hummingbird species i feeding on plant species j observed at time k and sampling event observed by transect (YTransect) or camera (YCamera)

Observation Model:

$$ YCamera_{i,j,k,d} \sim Binomial(N_{i,j,k},\omega_{Camera}) $$
$$ \omega_{Camera} <- \phi_{Camera} * EffortCamera_k $$

Process Model:

$$ N_{i,j,k} \sim Poisson(\lambda_{i,j,k}) $$
$$ log(\lambda_{i,j,k}) = \alpha_i + \beta_{1,i} * Traitmatch_{i,j} + \beta_{2,i} *Resources_k + \beta_{3,i} * Traitmatch_{i,j} * Resources_k $$

**Priors**

$$ \phi_{Camera} \sim U(0,1) $$
$$\alpha_i \sim Normal(\alpha_\mu,\alpha_\tau)$$
$$\beta_{1,i} \sim Normal(\mu_{\beta_1,\tau_{beta_1}})$$
$$\beta_{2,i} \sim Normal(\mu_{\beta_2,\tau_{beta_2}})$$
$$\beta_{3,i} \sim Normal(\mu_{\beta_3,\tau_{beta_3}})$$

Group Level Means
$$ \mu_\alpha \sim Normal(0,0.0001)$$
$$\mu_{\beta_1} \sim Normal(0,0.0001)$$
$$\mu_{\beta_2} \sim Normal(0,0.0001)$$
$$\mu_{\beta_3} \sim Normal(0,0.0001)$$

Group Level Variance
$$\tau_{\alpha} \sim Uniform(0,1000)$$
$$\tau_{\beta_1} \sim Uniform(0,1000)$$
$$\tau_{\beta_2} \sim Uniform(0,1000)$$
$$\tau_{\beta_3} \sim Uniform(0,1000)$$

```{r,eval=T,strip.white=T}
#Source model
source("Bayesian/NmixturePoissonRagged2m.R")

#print model
writeLines(readLines("Bayesian/NmixturePoissonRagged2m.R"))

#Inits
InitStage <- function(){
  #A blank Y matrix - all present
  initY<-array(dim=c(Birds,Plants,Times),max(indat$Camera)+1)
  initB<-rep(0.5,Birds)
list(S=initY,detect=initB)}

#Parameters to track
ParsStage <- c("alpha","beta1","beta2","beta3","alpha_mu","alpha_sigma","beta1_sigma","beta1_mu","beta2_mu","beta2_sigma","beta3_mu","beta3_sigma","dcam","dprior_cam","E","fit","fitnew")


#Jags Data
Dat<-list(
  Yobs_camera = indat$Camera,
  Birds=max(indat$jBird),
  Bird=indat$jBird,
  Plant=indat$jPlant,
  Time=indat$jID,
  Plants=max(indat$jPlant),
  Times=max(indat$jID),
  resources=resourceMatrix,
  Nobs=nrow(indat),
  Traitmatch=jTraitmatch)

  #MCMC options
  if(newModel){
    system.time(
      m2<-jags.parallel(data=Dat,parameters.to.save =ParsStage,inits=InitStage,model.file="Bayesian/NmixturePoissonRagged2m.jags",n.thin=2,n.iter=10,n.burnin=0,n.chains=2,DIC=F)
      )
  }
```

```{r,eval=F}
#recompile if needed
runs<-100000

recompile(m2)

if(!newModel){
  system.time(m2<-update(m2,n.iter=runs,n.burnin=runs-2000,n.thin=2))  
}

```

```{r}
#extract par to data.frame
pars_detect<-extract_par(m2,data=indat,Bird="jBird",Plant="jPlant")
```

##Assess Convergence

```{r,cache=FALSE,fig.width=13,fig.height=5}
###Chains
ggplot(pars_detect[pars_detect$par %in% c("alpha","beta1","beta2","beta3"),],aes(x=Draw,y=estimate,col=as.factor(Chain))) + geom_line() + facet_grid(par~species,scale="free") + theme_bw() + labs(col="Chain") + ggtitle("Species Level")
```

```{r,fig.height=5}
ggplot(pars_detect[pars_detect$par %in% c("dcam"),],aes(x=Draw,y=estimate,col=as.factor(Chain))) + geom_line() + facet_grid(species~par,scale="free") + theme_bw() + labs(col="Chain") + ggtitle("Species Level")
```

```{r,fig.height=5,fig.width=11}
ggplot(pars_detect[pars_detect$par %in% c("dprior_cam","beta1_mu","beta1_sigma","beta2_mu","beta2_sigma","beta3_mu","beta3_sigma","alpha_mu","alpha_sigma"),],aes(x=Draw,y=estimate,col=as.factor(Chain))) + geom_line() + theme_bw() + labs(col="Chain") + ggtitle("Group Level Parameters") + facet_wrap(~par,scales="free")
```

#Posteriors

```{r,cache=FALSE,fig.width=11,fig.height=14}
###Posterior Distributions
ggplot(pars_detect[pars_detect$par %in% c("alpha","beta1","beta2","beta3"),],aes(x=estimate)) + geom_histogram(position='identity') +  facet_grid(species~par,scales="free") + theme_bw() + ggtitle("Species Parameters")
```

```{r,cache=FALSE,fig.width=11,fig.height=8}
#Detection figure
pars_detect<-merge(pars_detect,jagsIndexBird,by.x="species",by.y="jBird",all=T)
ggplot(pars_detect[pars_detect$par %in% "dcam",],aes(x=par,y=estimate)) + geom_violin(fill='black') + theme_bw() + ggtitle("Detection Probability") + facet_wrap(~Hummingbird)
```

```{r,cache=FALSE,fig.height=5,fig.width=13}
```

#Detection Table
```{r}
detecttable<-group_by(pars_detect,Hummingbird,par) %>% filter(par %in% c('dcam')) %>% summarize(mean=mean(estimate),lower=quantile(estimate,0.05),upper=quantile(estimate,0.95))
detecttable
```

##Discrepancy 

The goodness of fit is a measured as chi-squared. The expected value for each day is the detection rate * the estimate intensity of interactions. The expected value is compared to the observed value of the actual data. In addition, a replicate dataset is generated from the posterior predicted intensity. Better fitting models will have lower discrepancy values and be 
Better fitting models are smaller values and closer to the 1:1 line. A perfect model would be 0 discrepancy. This is unrealsitic given the stochasticity in the sampling processes. Rather, its better to focus on relative discrepancy. In addition, a model with 0 discrepancy would likely be seriously overfit and have little to no predictive power.

```{r,fig.height=4,fig.width=8,message=F,warning=F}
fitstat<-pars_detect[pars_detect$par %in% c("fit","fitnew"),]
fitstat<-dcast(fitstat,Draw+Chain~par,value.var="estimate")

ymin<-round(min(fitstat$fit))
ymax<-round(max(fitstat$fit))
ab<-data.frame(x=0:ymax,y=0:ymax)
disc_obs<-ggplot(fitstat,aes(x=fit,y=fitnew)) + geom_point() + theme_bw() + labs(x="Discrepancy of observed data",y="Discrepancy of replicated data",col="Model")  + ggtitle("Posterior predictive check") + geom_line(data=ab,aes(x=x,y=y)) + coord_fixed() + ylim(ymin=0,ymax=max(max(c(fitstat$fit,fitstat$fitnew)))) + xlim(xmin=0,xmax=max(max(c(fitstat$fit,fitstat$fitnew))))
disc_obs

#Bayesian p-value
sum(fitstat$fitnew>fitstat$fit)/nrow(fitstat)
ggsave("Figures/ObservedDiscrepancy.jpeg",width = 5,height=10)
```

#Predicted Relationship 

```{r,fig.height=4,fig.width=4}
#Expand out pars
castdf<-dcast(pars_detect[pars_detect$par %in% c("beta1_mu","beta2_mu","beta3_mu","alpha_mu"),], Chain + Draw~par,value.var="estimate")
```

## Posterior prediction

```{r,fig.width=7,fig.height=6}
#Trajectories from posterior
predy<-trajF(alpha=castdf$alpha_mu,beta1=castdf$beta1_mu,trait=indat$Traitmatch,resources=indat$scaledR,beta2=castdf$beta2_mu,beta3=castdf$beta3_mu)

ggplot(data=predy,aes(x=trait)) + geom_ribbon(aes(ymin=lower,ymax=upper),alpha=0.4,fill="red")  +  theme_bw() + ylab("Interactions") + xlab("Difference between Bill and Corolla Length") + geom_point(data=indat,aes(x=Traitmatch,y=Camera)) + geom_line(aes(y=mean)) + geom_point(data=indat,aes(x=Traitmatch,y=Transect)) 
```

## At High and Low Resource Availability

```{r,fig.height=6,fig.width=10}

#Trajectories from posterior
predH<-trajF(alpha=castdf$alpha_mu,beta1=castdf$beta1_mu,trait=indat[indat$R=="High","Traitmatch"],resources=indat[indat$R=="High","scaledR"],beta2=castdf$beta2_mu,beta3=castdf$beta3_mu)

predM<-trajF(alpha=castdf$alpha_mu,beta1=castdf$beta1_mu,trait=indat[indat$R=="Medium","Traitmatch"],resources=indat[indat$R=="Medium","scaledR"],beta2=castdf$beta2_mu,beta3=castdf$beta3_mu)

predL<-trajF(alpha=castdf$alpha_mu,beta1=castdf$beta1_mu,trait=indat[indat$R=="Low","Traitmatch"],resources=indat[indat$R=="Low","scaledR"],beta2=castdf$beta2_mu,beta3=castdf$beta3_mu)

predhl<-melt(list(High=predH,Medium=predM,Low=predL),id.vars=colnames(predH))

colnames(predhl)[5]<-"BFlowerL"

predhl$BFlowerL<-factor(as.character(predhl$BFlowerL))
levels(predhl$BFlowerL)<-c("Low","Medium","High")

ggplot(data=predhl,aes(x=trait)) + geom_ribbon(aes(ymin=lower,ymax=upper,fill=BFlowerL),alpha=0.5)  + geom_line(aes(y=mean,col=BFlowerL),size=.8) + theme_bw() + ylab("Interactions") + xlab("Difference between Bill and Corolla Length") + geom_point(data=mindat,aes(x=Traitmatch,y=value))+ labs(fill="Resource Availability",col="Resource Availability") 
ggsave("Figures/AllRegression.jpeg",height=5,width=7)

```

##Species Predictions

```{r,fig.height=10,fig.width=11,eval=T}

castdf<-dcast(pars_detect[pars_detect$par %in% c("beta1","beta2","beta3","alpha"),], species +Chain +Draw ~par ,value.var="estimate")

#Turn to 
castdf$species<-factor(castdf$species,levels=1:max(as.numeric(castdf$species)))

species.split<-split(castdf,list(castdf$species),drop = T)

species.traj<-list()

for(d in 1:length(species.split)){
  x<-species.split[[d]]
  index<-unique(x$species)
  
  #get data for those species
  billd<-indat[indat$jBird %in% index,]

  #scale resources
  species.traj[[d]]<-trajF(alpha=x$alpha,beta1=x$beta1,beta2=x$beta2,beta3=x$beta3,resources=billd$scaledR,trait=billd$Traitmatch)
  }

names(species.traj)<-names(species.split)

species.traj<-melt(species.traj,id.var=colnames(species.traj[[1]]))

#split out names and model
species.traj[,c("Index")]<-colsplit(species.traj$L1,"\\.",c("Index"))

spe<-merge(species.traj,jagsIndexBird,by.x="Index",by.y="jBird")

#plot and compare to original data
ggplot(data=spe,aes(x=trait)) + geom_ribbon(aes(ymin=lower,ymax=upper),alpha=0.2,fill='red') + geom_line(aes(y=mean),size=.5) + theme_bw() + ylab("Daily Interaction Rate")+ xlab("Difference between Bill and Corolla Length") + facet_wrap(~Hummingbird,scales="free",ncol=4) + geom_point(data=mindat,aes(x=Traitmatch,y=value),size=2.5) 
```

###Species Predictions: High and Low Availability

```{r,fig.height=10,fig.width=11,eval=T}

castdf<-dcast(pars_detect[pars_detect$par %in% c("beta1","beta2","beta3","alpha"),], species +Chain +Draw ~par ,value.var="estimate")

#Turn to 
castdf$species<-factor(castdf$species,levels=1:max(as.numeric(castdf$species)))

species.split<-split(castdf,list(castdf$species),drop = T)

species.traj<-list()

for(d in 1:length(species.split)){
  x<-species.split[[d]]
  index<-unique(x$species)
  
  #get data for those species
  billd<-indat[indat$jBird %in% index,]

  sh<-trajF(alpha=x$alpha,beta1=x$beta1,beta2=x$beta2,beta3=x$beta3,resources=billd[billd$R=="High","scaledR"],trait=billd[billd$R=="High","Traitmatch"])
  
  sm<-trajF(alpha=x$alpha,beta1=x$beta1,beta2=x$beta2,beta3=x$beta3,resources=billd[billd$R=="Medium","scaledR"],trait=billd[billd$R=="Medium","Traitmatch"])

  sl<-trajF(alpha=x$alpha,beta1=x$beta1,beta2=x$beta2,beta3=x$beta3,resources=billd[billd$R=="Low","scaledR"],trait=billd[billd$R=="Low","Traitmatch"])
  
  sm<-melt(list(High=sh,Medium=sm,Low=sl),id.vars=colnames(sl))
  colnames(sm)[5]<-"Resources"
  species.traj[[d]]<-sm
  }

names(species.traj)<-names(species.split)

species.traj<-melt(species.traj,id.var=colnames(species.traj[[1]]))

#split out names and model
species.traj[,c("Index")]<-colsplit(species.traj$L1,"\\.",c("Index"))

spe<-merge(species.traj,jagsIndexBird,by.x="Index",by.y="jBird")

#plot and compare to original data
indat$rplot<-as.factor(indat$scaledR)
levels(indat$rplot)<-c("Low","Medium","High")
ggplot(data=spe,aes(x=trait)) + geom_ribbon(aes(ymin=lower,ymax=upper,fill=Resources),alpha=0.2) + geom_line(aes(y=mean,col=Resources),size=.5) + theme_bw() + ylab("Daily Interaction Rate")+ xlab("Difference between Bill and Corolla Length") + facet_wrap(~Hummingbird,scales="free",ncol=4) + geom_point(data=indat,aes(x=Traitmatch,y=Yobs,col=rplot),size=4,alpha=.75)
ggsave("Figures/SpeciesRegression.jpeg",height=6,width=7)

```

##Species Level Interaction

```{r,fig.height=11,fig.width=10,eval=F}
castdf<-dcast(pars_detect[pars_detect$par %in% c("beta1","beta2","beta3","alpha"),], species +Chain + Draw~par,value.var="estimate")

#Turn to 
castdf$species<-factor(castdf$species,levels=1:max(as.numeric(castdf$species)))

species.split<-split(castdf,list(castdf$species),drop = T)

species.traj<-list()

for(d in 1:length(species.split)){
  dat<-species.split[[d]]
  index<-unique(dat$species)
  
  #get data for those species
  billd<-mindat[mindat$jBird %in% index,]

  #Calculate interaction effect
  species.traj[[d]]<-intF(alpha=dat$alpha,beta1=dat$beta1,x=billd[billd$value > 0 & !is.na(billd$value),'Traitmatch'],resources=billd[billd$value > 0 & !is.na(billd$value),'scaledR'],beta2=dat$beta2,beta3=dat$beta3)
  }

names(species.traj)<-names(species.split)
species.traj<-melt(species.traj,id.var=colnames(species.traj[[1]]))

#split out names and model
species.traj[,c("Index")]<-colsplit(species.traj$L1,"\\.",c("Index"))

spe<-merge(species.traj,jagsIndexBird,by.x="Index",by.y="jBird")

#match colnames

#plot and compare to original data
ggplot(data=spe,aes(x=x)) + geom_ribbon(aes(ymin=lower,ymax=upper,fill=Hummingbird),alpha=0.3) + geom_line(aes(y=mean,col=Hummingbird),size=1) + theme_bw() + xlab("Difference between Bill and Corolla Length")  + ylab("Effect of Resources on Trait Difference") + facet_wrap(~Hummingbird,scales="free",ncol=3)
ggsave("Figures/SpeciesInteraction.jpeg",height=6,width=7)
```

These plots can be tricky to interpret if one forgets that trait matching as a covariate is a distance. Therefore remember that a positive slope in the plot above indiciates, "As resources increase species use flowers less similiar to their bill lengths". 

## Which species did we predict well?
```{r}
smat<-pars_detect %>% filter(par=="E") %>% group_by(species) %>% summarize(fit=sum(estimate)) %>% arrange(desc(fit))
smat<-merge(smat,jagsIndexBird,by.x="species",by.y="jBird")
smat
```

## Discrepancy matrix

```{r}
dmat<-pars_detect %>% filter(par=="E") %>% group_by(species,plant) %>% summarize(fit=sum(estimate)) %>% arrange(desc(fit))
dmat<-merge(dmat,jagsIndexBird,by.x="species",by.y="jBird")
dmat<-merge(dmat,jagsIndexPlants,by.x="plant",by.y="jPlant")
head(dmat,10)

#get order
hord<-dmat %>% group_by(Hummingbird) %>% summarize(n=sum(fit)) %>% arrange(desc(n)) %>% .$Hummingbird
pord<-dmat %>% group_by(Iplant_Double) %>% summarize(n=sum(fit)) %>% arrange(n) %>%  .$Iplant_Double
dmat$Hummingbird<-factor(dmat$Hummingbird,levels=hord)
dmat$Iplant_Double<-factor(dmat$Iplant_Double,levels=pord)
ggplot(dmat,aes(x=Hummingbird,Iplant_Double,fill=fit)) + geom_tile() + theme_bw() + scale_fill_continuous("Discrepancy",low="blue",high="red")
```


##Resource Abundance Functions
Let's take a closer look at distribution of interaction effect posteriors values for each species.

```{r,eval=T}
post<-pars_detect %>% filter(par %in% "beta2") %>% group_by(Hummingbird) %>% summarize(mean=mean(estimate),median=median(estimate),lower=quantile(probs=0.025,estimate),upper=quantile(probs=0.975,estimate)) %>% melt(id.vars='Hummingbird')
ggplot(pars_detect[pars_detect$par %in% "beta2",],aes(x=estimate)) + geom_histogram() + facet_wrap(~Hummingbird,scales='free',ncol=4) + geom_vline(data=post,aes(xintercept=value,col=variable))
```

##Interaction density functions
Let's take a closer look at distribution of interaction effect posteriors values for each species.

```{r,eval=T}
post<-pars_detect %>% filter(par %in% "beta3") %>% group_by(Hummingbird) %>% summarize(mean=mean(estimate),median=median(estimate),lower=quantile(probs=0.025,estimate),upper=quantile(probs=0.975,estimate)) %>% melt(id.vars='Hummingbird')
ggplot(pars_detect[pars_detect$par %in% "beta3",],aes(x=estimate)) + geom_histogram() + facet_wrap(~Hummingbird,scales='free',ncol=4) + geom_vline(data=post,aes(xintercept=value,col=variable))
```

##Trait-matching and Bill Length

Do species with long bill lengths have positive traitmatching effects?

```{r,fig.height=7,fig.width=8}
#species names
b<-pars_detect[pars_detect$par %in% "beta1",]

#traits
b<-merge(b,hum.morph,by.x="Hummingbird",by.y="English")

post<-b %>% filter(par %in% "beta1") %>% group_by(Hummingbird) %>% summarize(mean=mean(estimate),median=median(estimate),lower=quantile(probs=0.025,estimate),upper=quantile(probs=0.975,estimate),quantile_l=quantile(estimate)[[1]],quantile_u=quantile(estimate)[[2]]) %>% melt(id.vars='Hummingbird')

#get order of mean posterior
ord<-post %>% filter(variable=="mean") %>% arrange(value) %>% .$Hummingbird

b$Hummingbird<-factor(b$Hummingbird,levels=ord)
ggplot(b,aes(y=estimate,x=as.factor(Total_Culmen),group=Hummingbird)) + geom_violin(fill='grey50') + coord_flip()  + ggtitle("Trait-matching and Bill Length") + theme_bw()
```

##Interaction and Bill Length

Do species with long bill lengths have positive interaction effects?

```{r,fig.height=7,fig.width=8,eval=F}
#species names
b<-pars_detect[pars_detect$par %in% "beta3",]

#traits
b<-merge(b,hum.morph,by.x="Hummingbird",by.y="English")

post<-b %>% filter(par %in% "beta3") %>% group_by(Hummingbird) %>% summarize(mean=mean(estimate),median=median(estimate),lower=quantile(probs=0.025,estimate),upper=quantile(probs=0.975,estimate),quantile_l=quantile(estimate)[[1]],quantile_u=quantile(estimate)[[2]]) %>% melt(id.vars='Hummingbird')

#get order of mean posterior
ord<-post %>% filter(variable=="mean") %>% arrange(value) %>% .$Hummingbird

b$Hummingbird<-factor(b$Hummingbird,levels=ord)
ggplot(b,aes(y=estimate,x=Hummingbird,fill=Total_Culmen)) + geom_violin() + coord_flip() + scale_fill_continuous(low='blue',high='red') + ggtitle("Interaction Effect and Bill Length") + theme_bw()

```

#Estimated niche breadth

```{r}
castdf<-dcast(pars_detect[pars_detect$par %in% c("beta1","beta2","beta3","alpha"),], species +Chain + Draw~par,value.var="estimate")

#Turn to 
castdf$species<-factor(castdf$species,levels=1:max(as.numeric(castdf$species)))

species.split<-split(castdf,list(castdf$species),drop = T)

species.traj<-lapply(species.split,function(dat){
  index<-unique(dat$species)
  
  #get data for those species
  billd<-indat[indat$jBird %in% index,]
  
  d<-data.frame(alpha=dat$alpha,beta1=dat$beta1,beta2=dat$beta2,beta3=dat$beta3)
  
  #fit regression for each input estimate
  sampletraj<-list()
  
  for (y in 1:nrow(d)){
    v=exp(d$alpha[y] + d$beta1[y] * billd$Traitmatch + d$beta2[y] * billd$scaledR + d$beta3[y] * billd$Traitmatch*billd$scaledR)
    
    sampletraj[[y]]<-data.frame(x=as.numeric(billd$Traitmatch),y=as.numeric(v),r=as.numeric(billd$scaledR),jBird=billd$jBird,jPlant=billd$jPlant,jTime=billd$jTime)
  }
  
  sample_all<-rbind_all(sampletraj)
})
  
species.traj<-rbind_all(species.traj)
```

Mean Estimates for Corolla Sizes

```{r}
species.mean<-species.traj %>% group_by(jBird,jPlant,r) %>% summarize(Traitmatch=unique(x),phi=mean(y))

tomerge<-indat %>% select(jBird,jPlant,Hummingbird,Iplant_Double) %>% distinct()

species.mean<-merge(species.mean,tomerge)

#get corolla sizes
species.mean<-merge(species.mean,fl.morph,by.x="Iplant_Double", by.y="Group.1")

#bill order
ord<-hum.morph %>% arrange(Total_Culmen) %>% .$English
species.mean$Hummingbird<-factor(species.mean$Hummingbird,levels=ord)

#add level to hum.morph to match naming convention
species.mean<-merge(species.mean,hum.morph[,c("English","Total_Culmen")],by.x="Hummingbird",by.y="English")

p<-ggplot(species.mean,aes(x=Corolla,y=phi,col=as.factor(r))) + geom_line(size=.9) + geom_vline(aes(xintercept=Total_Culmen),linetype='dashed') + facet_wrap(~Hummingbird,ncol=3,scales="free_y")  + theme_bw() + ylab("Probability of Interaction") + scale_color_manual("Resource Availability",labels=c("Low","Medium","High"),values=c("Black","Blue","Red")) + xlab("Flower Corolla Length (mm)") 
p
ggsave("Figures/ResponseCurves.jpeg",height=6.5,width=9)
```

#Niche Breadth 

```{r}
species.mean<-species.traj %>% group_by(jBird,jPlant,r) %>% summarize(Traitmatch=unique(x),phi=mean(y),phi_low=quantile(y,0.05),phi_high=quantile(y,0.95))

#merge names
species.mean<-merge(species.mean,jagsIndexBird)
species.mean<-merge(species.mean,jagsIndexPlants)

#get corolla sizes
species.mean<-merge(species.mean,fl.morph,by.x="Iplant_Double", by.y="Group.1")

#bill order
ord<-hum.morph %>% arrange(Total_Culmen) %>% .$English
species.mean$Hummingbird<-factor(species.mean$Hummingbird,levels=ord)

#add level to hum.morph to match naming convention
species.mean<-merge(species.mean,hum.morph[,c("English","Total_Culmen")],by.x="Hummingbird",by.y="English")

#label factor
species.mean$r<-as.factor(species.mean$r)
levels(species.mean$r)<-c("Low","Medium","High")
ggplot(species.mean) + geom_ribbon(alpha=0.7,aes(x=Corolla,ymin=phi_low,ymax=phi_high,fill=r)) + theme_bw() + facet_wrap(~Hummingbird,scales="free",ncol=4)+ ggtitle("Niche Breadth") + geom_vline(aes(xintercept=Total_Culmen),linetype='dashed') + geom_line(aes(x=Corolla,y=phi,fill=r)) + ylab("Probability of Interaction") + xlab("Corolla Length (mm)") + scale_fill_manual("Resource Availability",values=c("Grey70","Grey20","Black"))
ggsave("Figures/NicheBreadth.jpeg",height=8,width=9)
```

##Range plots

```{r}
nsplit<-split(species.mean,species.mean$r)
makeR<-function(x){
  
  #input matrix
  aggm<-matrix(nrow=nrow(jagsIndexBird),ncol=nrow(jagsIndexPlants),data=0)
  for (j in 1:nrow(x)){
    aggm[x[j,"jBird"],x[j,"jPlant"]]<-rpois(1,lambda=x[j,"phi"])
  }
  
  aggm<-melt(aggm)
  colnames(aggm)<-c("jBird","jPlant","P")
  tomerge<-species.mean %>% select(jBird,jPlant,Corolla,Hummingbird,Traitmatch) %>% distinct()
  aggm<-merge(aggm,tomerge)
  return(aggm)
}

nstat<-lapply(nsplit,function(x){
  netstat<-melt(lapply(1:50,function(k) makeR(x)),id.vars=c("jBird","jPlant","Hummingbird","Traitmatch","Corolla","P"))
  colnames(netstat)[7]<-"Iteration"
  return(netstat)
})

names(nstat)<-c("Low","Medium","High")
nstat<-melt(nstat,colnames(nstat[[1]]))
```

Predicted density

```{r}
ggplot(nstat[nstat$P==1,],aes(x=Corolla,fill=L1)) + geom_density(alpha=0.6) + facet_wrap(~Hummingbird,scales='free',nrow=5) + scale_fill_discrete("Resource Availability") + theme_bw()
```

```{r,fig.width=6,fig.height=10}
rangestat<-nstat %>% filter(P==1) %>% group_by(Hummingbird,L1) %>% summarize(mean=mean(Corolla),lower=quantile(Corolla,0.05),upper=quantile(Corolla,0.95))
  
ggplot(rangestat,aes(x=Hummingbird,ymin=lower,ymax=upper,ymean=mean,col=L1)) + geom_linerange(alpha=0.5,position=position_dodge(width=.75),size=2) + geom_point(aes(y=mean),position=position_dodge(width=.75)) + labs(col="Resource Availability",y="Corolla Length (mm)") + theme_bw() + coord_flip() + theme(legend.position="bottom")
```

### Predicted Mean

```{r}
meanstat<-nstat %>% filter(P==1) %>% group_by(Hummingbird,L1,Iteration) %>% summarize(a=mean(Corolla))%>% summarize(mean=mean(a),lower=quantile(a,0.05),upper=quantile(a,0.95))
  
ggplot(meanstat,aes(x=Hummingbird,ymin=lower,ymax=upper,ymean=mean,col=L1)) + geom_linerange(alpha=0.5,position=position_dodge(width=.6),size=2) + geom_point(aes(y=mean),position=position_dodge(width=.6)) + labs(col="Resource Availability",y="Corolla Length (mm)") + theme_bw() + coord_flip() + theme(legend.position="bottom")
```

### Predicted Min

```{r}
meanstat<-nstat %>% filter(P==1) %>% group_by(Hummingbird,L1,Iteration) %>% summarize(a=min(Corolla))%>% summarize(mean=mean(a),lower=quantile(a,0.05),upper=quantile(a,0.95))
  
ggplot(meanstat,aes(x=Hummingbird,ymin=lower,ymax=upper,ymean=mean,col=L1)) + geom_linerange(alpha=0.5,position=position_dodge(width=.75),size=2) + geom_point(aes(y=mean),position=position_dodge(width=.75)) + labs(col="Resource Availability",y="Corolla Length (mm)") + theme_bw() + coord_flip() + theme(legend.position="bottom")
```

### Predicted Max

```{r}
meanstat<-nstat %>% filter(P==1) %>% group_by(Hummingbird,L1,Iteration) %>% summarize(a=min(Corolla))%>% summarize(mean=mean(a),lower=quantile(a,0.05),upper=quantile(a,0.95))
  
ggplot(meanstat,aes(x=Hummingbird,ymin=lower,ymax=upper,ymean=mean,col=L1)) + geom_linerange(alpha=0.5,position=position_dodge(width=.6),size=2) + geom_point(aes(y=mean),position=position_dodge(width=.6)) + labs(col="Resource Availability",y="Corolla Length (mm)") + theme_bw() + coord_flip() + theme(legend.position="bottom")
```

#Generate network

```{r}
#Split by resource
nsplit<-split(species.mean,species.mean$r)

makeN<-function(x){
  
  #input matrix
  aggm<-matrix(nrow=nrow(jagsIndexBird),ncol=nrow(jagsIndexPlants),data=0)
  for (j in 1:nrow(x)){
    aggm[x[j,"jBird"],x[j,"jPlant"]]<-rpois(1,lambda=x[j,"phi"])
  }
  #calculate network statistic
  nstat<-networklevel(aggm,index=c("weighted connectance","weighted NODF","niche overlap"),level="lower")
}

nstat<-lapply(nsplit,function(x){
  netstat<-melt(t(sapply(1:500,function(k) makeN(x)))) 
  colnames(netstat)<-c("Iteration","Metric","value")
  return(netstat)
})

names(nstat)<-c("Low","Medium","High")
nstat<-melt(nstat,colnames(nstat[[1]]))

ggplot(nstat,aes(x=value,fill=L1)) + geom_density(alpha=0.6) + facet_wrap(~Metric,scales='free',nrow=3) + scale_fill_discrete("Resource Availability") + theme_bw()
ggsave("Figures/NetworkStatistics.jpeg",height=5,width=6,dpi=600)
```

Compared to raw visits
```{r}
sindat<-split(indat,indat$scaledR)
ndat<-lapply(sindat,function(x){
  web<-acast(x[x$Yobs==1,],Hummingbird~Iplant_Double,value.var = "Yobs", fun= function(x){ length(unique(x))})
  nstat<-t(networklevel(web,index=c("weighted connectance","weighted NODF","niche overlap"),level="lower"))
})
names(ndat)<-c("Low","Medium","High")
ndat<-melt(ndat)

colnames(ndat)<-c("Var1","Metric","value","L1")

ggplot(nstat,aes(x=value,fill=L1)) + geom_density(alpha=0.6) + facet_wrap(~Metric,scales='free',nrow=2) + scale_fill_discrete("Resource Availability") + geom_vline(data=ndat,aes(xintercept=value,col=L1),linetype="dashed") + scale_color_discrete(guide='none')
```

```{r}
save.image("ObservedModel.RData")
```
