---
title: "Observed2M_Model"
author: "Ben Weinstein"
date: "June 6, 2016"
output: html_document
---


```{r,warning=FALSE,message=FALSE,echo=FALSE,cache=FALSE}
library(reshape2)
library(foreach)
library(doSNOW)
library(chron)
library(ggplot2)
library(knitr)
library(R2jags)
library(dplyr)
library(stringr)
library(gridExtra)
library(boot)
library(picante)
library(bipartite)

opts_chunk$set(message=FALSE,warning=FALSE,fig.width=10,fig.height=7,echo=TRUE,cache=F,fig.align='center',fig.path="figureObserved/")

set.seed(3)

#source functions
source("Bayesian/BayesFunctions.R")
```

```{r,echo=F,cache=FALSE}
paste("Run Completed at",Sys.time())
```

```{r}
#Load in data from Observed2m_Generate.Rmd
load("Observed.RData")
```

#Hierarchical Occupancy Model

For hummingbird species i feeding on plant species j observed at time k and sampling event d. 

$$ YTransect_{i,j,k,d} \sim Bernoulli(\omega_{Transect}) $$

$$ YCamera_{i,j,k,d} \sim Bernoulli(\omega_{Camera}) $$
$$ \omega_{Camera} <- \phi_{Camera} * EffortCamera_k $$
$$ \omega_{Transect} <- \phi_{Transect}* EffortTransect_k $$
$$ p_{i,j,k} \sim Bernoulli(\rho_{i,j,k}) $$
$$ logit(\rho_{i,j,k}) = \alpha_i + \beta_{1,i} * Traitmatch_{i,j} + \beta_{2,i} *Resources_k + \beta_{3,i} * Traitmatch_{i,j} * Resources_k $$

**Priors**

$$ \phi_{Camera} \sim U(0,1) $$
$$ \phi_{Transect} \sim U(0,1) $$
$$\alpha_i \sim Normal(\alpha_mu,\alpha_{\tau})$$
$$\beta_{1,i} \sim Normal(\mu_\beta_1,\tau_beta_1)$$
$$\beta_{2,i} \sim Normal(\mu_\beta_2,\tau_beta_2)$$
$$\beta_{3,i} \sim Normal(\mu_\beta_3,\tau_beta_3)$$

**Hyperpriors**

Group Level Means
$$ \mu_\alpha \sim Normal(0,0.0001)$$

$$\mu_\beta_1 \sim Normal(0,0.0001)$$
$$\mu_\beta_2} \sim Normal(0,0.0001)$$
$$\mu_\beta_3 \sim Normal(0,0.0001)$$

Group Level Variance

$$\tau_{\alpha} \sim Half-Cauchy(0,1,1)$$
$$\tau_\beta_1 \sim Half-Cauchy(0,1,1)$$
$$\tau_\beta_2 \sim Half-Cauchy(0,1,1)$$
$$\tau_\beta_3 \sim Half-Cauchy(0,1,1)$$

```{r,eval=T,strip.white=T}

#Source model
source("Bayesian/NmixturePoissonRagged2m.R")

#print model
writeLines(readLines("Bayesian/NmixturePoissonRagged2m.R"))

#Input Data
Dat <- c('Yobs_camera','Yobs_transect','Birds','Bird','Plant','Time','Plants','Times','resources','Nobs','cam_surveys','trans_surveys','Traitmatch')

#Inits
InitStage <- function(){
  #A blank Y matrix - all present
  initY<-array(dim=c(Birds,Plants,Times),1)
  initB<-as.numeric(matrix(nrow=Birds,ncol=1,data=0))
  initD<-as.numeric(matrix(nrow=Birds,ncol=1,data=.5))

list(beta1=initB,beta2=initB,alpha=rep(.5,Birds),intercept=0,tau_alpha=0.1,tau_beta1=0.1,tau_beta2=0.1,gamma1=0,gamma2=0)}

#Parameters to track
ParsStage <- c("alpha","beta1","beta2","intercept","sigma_int","sigma_slope1","sigma_slope2","sigma_slope3","gamma1","gamma2","dtrans","dcam")

#Jags Data

  Yobs_camera = indat$Camera
  Yobs_transect = indat$Transect
  Birds=max(indat$jBird)
  Bird=indat$jBird
  Plant=indat$jPlant
  Time=indat$jID
  Plants=max(indat$jPlant)
  Times=max(indat$jID)
  resources=resourceMatrix
  Nobs=nrow(indat)
  cam_surveys= cam_effort
  trans_surveys= trans_effort
  Traitmatch=jTraitmatch

#MCMC options

  system.time(m2<-jags(data=Dat,parameters.to.save =ParsStage,model.file="Bayesian/NmixturePoissonRagged2m.jags",n.thin=1,n.iter=100,n.burnin=0,n.chains=1))
```

```{r,eval=F}
#recompile if needed
load.module("dic")
runs<-40000
recompile(m2)
m2<-update(m2,n.iter=runs,n.burnin=runs*.9,n.thin=3)
```

```{r}
#extract par to data.frame
pars_detect<-extract_par(m2,data=indat,Bird="jBird",Plant="jPlant")
```

##Assess Convergence

```{r,cache=FALSE,fig.width=13,fig.height=5}
###Chains
ggplot(pars_detect[pars_detect$par %in% c("alpha","beta1"," beta2"),],aes(x=Draw,y=estimate,col=as.factor(Chain))) + geom_line() + facet_grid(par~species,scale="free") + theme_bw() + labs(col="Chain") + ggtitle("Species Level")
```

```{r,fig.height=10}
ggplot(pars_detect[pars_detect$par %in% c("dcam","dtrans"),],aes(x=Draw,y=estimate,col=as.factor(Chain))) + geom_line() + facet_wrap(~par,scale="free",ncol=4) + theme_bw() + labs(col="Chain") + ggtitle("Species Level")
```

```{r,fig.height=5,fig.width=11}
ggplot(pars_detect[pars_detect$par %in% c("gamma1","intercept","sigma_int","sigma_slope1","gamma2","sigma_slope2"),],aes(x=Draw,y=estimate,col=as.factor(Chain))) + geom_line() + theme_bw() + labs(col="Chain") + ggtitle("Group Level Parameters") + facet_wrap(~par,scales="free")
```

#Posteriors

```{r,cache=FALSE,fig.width=11,fig.height=14}
###Posterior Distributions
ggplot(pars_detect[pars_detect$par %in% c("alpha","beta1","beta2"),],aes(x=estimate)) + geom_histogram(position='identity') +  facet_grid(species~par,scales="free") + theme_bw() + ggtitle("Species Parameters")
#overlay priors
```

```{r,cache=FALSE,fig.width=10,fig.height=10}
#Detection figure
ggplot(pars_detect[pars_detect$par %in% c("dtrans","dcam"),],aes(x=par,y=estimate)) + geom_violin(fill='black') + theme_bw() + ggtitle("Detection Probability") + scale_x_discrete(labels=c("Camera","Transect"))
```

```{r,cache=FALSE,fig.height=5,fig.width=13}
ggplot(pars_detect[pars_detect$par %in% c("gamma1","gamma2","intercept","sigma_int","sigma_slope1","sigma_slope2"),],aes(x=estimate)) + geom_histogram() + ggtitle("Group Level Posteriors") + facet_wrap(~par,scale="free",nrow=2) + theme_bw() 
```

#Predicted Relationship 

```{r,fig.height=4,fig.width=4}
#Expand out pars
castdf<-dcast(pars_detect[pars_detect$par %in% c("gamma1","gamma2","intercept"),], Chain + Draw~par,value.var="estimate")
```

## Posterior prediction

```{r,fig.width=7,fig.height=6}
#Trajectories from posterior
predy<-trajF(alpha=castdf$intercept,beta1=castdf$gamma1,x=indat$Traitmatch,resources=indat$scaledR,beta2=castdf$gamma2,beta3=0,type='quantile')

ggplot(data=predy,aes(x=x)) + geom_ribbon(aes(ymin=lower,ymax=upper),alpha=0.4,fill="red")  +  theme_bw() + ylab("Interactions") + xlab("Difference between Bill and Corolla Length") + geom_point(data=indat,aes(x=Traitmatch,y=Camera)) + geom_line(aes(y=mean)) + geom_point(data=indat,aes(x=Traitmatch,y=Transect)) 
```

## At High and Low Resource Availability

```{r,fig.height=6,fig.width=10}

#Trajectories from posterior
predH<-trajF(alpha=castdf$intercept,beta1=castdf$gamma1,x=indat[indat$ BUsed_Flowers==1,"Traitmatch"],resources=indat[indat$ BUsed_Flowers==1,"scaledR"],beta2=castdf$gamma2,beta3=0,type='quantile')

predL<-trajF(alpha=castdf$intercept,beta1=castdf$gamma1,x=indat[indat$ BUsed_Flowers==0,"Traitmatch"],resources=indat[indat$ BUsed_Flowers==0,"scaledR"],beta2=castdf$gamma2,beta3=0,type='quantile')

predhl<-melt(list(High=predH,Low=predL),id.vars=colnames(predH))

colnames(predhl)[5]<-"BFlowerL"

indat$BFlowerL<-factor(as.character(indat$ BUsed_Flowers))
levels(indat$BFlowerL)<-c("Low","High")

ggplot(data=predhl,aes(x=x)) + geom_ribbon(aes(ymin=lower,ymax=upper,fill=BFlowerL),alpha=0.2)  + geom_line(aes(y=mean,col=BFlowerL),size=.8) + theme_bw() + ylab("Interactions") + xlab("Difference between Bill and Corolla Length") + geom_point(data=mindat,aes(x=Traitmatch,y=value))+ labs(fill="Resource Availability",col="Resource Availability") 
ggsave("Figures/AllRegression.jpeg",height=5,width=7)

```

##Species Predictions

```{r,fig.height=10,fig.width=11,eval=T}

castdf<-dcast(pars_detect[pars_detect$par %in% c("beta1","beta2","alpha"),], species +Chain +Draw ~par ,value.var="estimate")

#Turn to 
castdf$species<-factor(castdf$species,levels=1:max(as.numeric(castdf$species)))

species.split<-split(castdf,list(castdf$species),drop = T)

species.traj<-list()

for(d in 1:length(species.split)){
  x<-species.split[[d]]
  index<-unique(x$species)
  
  #get data for those species
  billd<-indat[indat$jBird %in% index,]

  #scale resources
  species.traj[[d]]<-trajF(alpha=x$alpha,beta1=x$beta1,beta2=x$beta2,beta3=0,resources=billd$scaledR,x=billd$Traitmatch,type='quantile')
  }

names(species.traj)<-names(species.split)

species.traj<-melt(species.traj,id.var=colnames(species.traj[[1]]))

#split out names and model
species.traj[,c("Index")]<-colsplit(species.traj$L1,"\\.",c("Index"))

spe<-merge(species.traj,jagsIndexBird,by.x="Index",by.y="jBird")

#plot and compare to original data
ggplot(data=spe,aes(x=x)) + geom_ribbon(aes(ymin=lower,ymax=upper),alpha=0.2,fill='red') + geom_line(aes(y=mean),size=.5) + theme_bw() + ylab("Occurrence Probability")+ xlab("Difference between Bill and Corolla Length") + facet_wrap(~Hummingbird,scales="free",ncol=4) + geom_point(data=mindat,aes(x=Traitmatch,y=value,shape=variable),size=2.5) + labs(shape="Sampling Method")
```

###Species Predictions: High and Low Availability

```{r,fig.height=10,fig.width=11,eval=T}

castdf<-dcast(pars_detect[pars_detect$par %in% c("beta1","beta2","beta3","alpha"),], species +Chain +Draw ~par ,value.var="estimate")

#Turn to 
castdf$species<-factor(castdf$species,levels=1:max(as.numeric(castdf$species)))

species.split<-split(castdf,list(castdf$species),drop = T)

species.traj<-list()

for(d in 1:length(species.split)){
  x<-species.split[[d]]
  index<-unique(x$species)
  
  #get data for those species
  billd<-indat[indat$jBird %in% index,]

  sl<-trajF(alpha=x$alpha,beta1=x$beta1,beta2=x$beta2,beta3=0,resources=billd[billd$ BUsed_Flowers==0,"scaledR"],x=billd[billd$ BUsed_Flowers==0,"Traitmatch"],type='quantile')
  sh<-trajF(alpha=x$alpha,beta1=x$beta1,beta2=x$beta2,beta3=0,resources=billd[billd$ BUsed_Flowers==1,"scaledR"],x=billd[billd$ BUsed_Flowers==1,"Traitmatch"],type='quantile')
  sm<-melt(list(High=sh,Low=sl),id.vars=colnames(sl))
  colnames(sm)[5]<-"Resources"
  species.traj[[d]]<-sm
  }

names(species.traj)<-names(species.split)

species.traj<-melt(species.traj,id.var=colnames(species.traj[[1]]))

#split out names and model
species.traj[,c("Index")]<-colsplit(species.traj$L1,"\\.",c("Index"))

spe<-merge(species.traj,jagsIndexBird,by.x="Index",by.y="jBird")

#plot and compare to original data
ggplot(data=spe,aes(x=x)) + geom_ribbon(aes(ymin=lower,ymax=upper,fill=Resources),alpha=0.2) + geom_line(aes(y=mean,col=Resources),size=.5) + theme_bw() + ylab("Occurrence Probability")+ xlab("Difference between Bill and Corolla Length") + facet_wrap(~Hummingbird,scales="free",ncol=3) + geom_point(data=mindat,aes(x=Traitmatch,y=value,shape=variable),size=1.5,alpha=.5)
ggsave("Figures/SpeciesRegression.jpeg",height=6,width=7)

```

##Species Level Interaction

```{r,fig.height=11,fig.width=10,eval=T}
castdf<-dcast(pars_detect[pars_detect$par %in% c("beta1","beta2","beta3","alpha"),], species +Chain + Draw~par,value.var="estimate")

#Turn to 
castdf$species<-factor(castdf$species,levels=1:max(as.numeric(castdf$species)))

species.split<-split(castdf,list(castdf$species),drop = T)

species.traj<-list()

for(d in 1:length(species.split)){
  dat<-species.split[[d]]
  index<-unique(dat$species)
  
  #get data for those species
  billd<-mindat[mindat$jBird %in% index,]

  #Calculate interaction effect
  species.traj[[d]]<-intF(alpha=dat$alpha,beta1=dat$beta1,x=billd[billd$value > 0 & !is.na(billd$value),'Traitmatch'],resources=billd[billd$value > 0 & !is.na(billd$value),'scaledR'],beta2=dat$beta2,beta3=0,type='quantile')
  
  }

names(species.traj)<-names(species.split)
species.traj<-melt(species.traj,id.var=colnames(species.traj[[1]]))

#split out names and model
species.traj[,c("Index")]<-colsplit(species.traj$L1,"\\.",c("Index"))

spe<-merge(species.traj,jagsIndexBird,by.x="Index",by.y="jBird")

#match colnames

#plot and compare to original data
ggplot(data=spe,aes(x=x)) + geom_ribbon(aes(ymin=lower,ymax=upper,fill=Hummingbird),alpha=0.3) + geom_line(aes(y=mean,col=Hummingbird),size=1) + theme_bw() + xlab("Difference between Bill and Corolla Length")  + ylab("Effect of Resources on Trait Difference") + facet_wrap(~Hummingbird,scales="free",ncol=3)
ggsave("Figures/SpeciesInteraction.jpeg",height=6,width=7)

```

These plots can be tricky to interpret if one forgets that trait matching as a covariate is a distance. Therefore remember that a positive slope in the plot above indiciates, "As resources increase species use flowers less similiar to their bill lengths". 

##Interaction density functions
Let's take a closer look at distribution of interaction effect posteriors values for each species.

```{r}
post<-pars_detect %>% filter(par %in% "beta3") %>% group_by(species) %>% summarize(mean=mean(estimate),median=median(estimate),lower=quantile(probs=0.025,estimate),upper=quantile(probs=0.975,estimate),quantile_l=quantile(estimate)[[1]],quantile_u=quantile(estimate)[[2]]) %>% melt(id.vars='species')
ggplot(pars_detect[pars_detect$par %in% "beta3",],aes(x=estimate)) + geom_histogram() + facet_wrap(~species,scales='free',ncol=3) + geom_vline(data=post,aes(xintercept=value,col=variable))
```

##Traitmatching and Bill Length

Do species with long bill lengths have positive traitmatching effects?

```{r,fig.height=7,fig.width=8}
#species names
b<-pars_detect[pars_detect$par %in% "beta1",]
b<-merge(b,jagsIndexBird,by.x="species",by.y="jBird")

#traits
b<-merge(b,hum.morph,by.x="Hummingbird",by.y="English")

post<-b %>% filter(par %in% "beta1") %>% group_by(Hummingbird) %>% summarize(mean=mean(estimate),median=median(estimate),lower=quantile(probs=0.025,estimate),upper=quantile(probs=0.975,estimate),quantile_l=quantile(estimate)[[1]],quantile_u=quantile(estimate)[[2]]) %>% melt(id.vars='Hummingbird')

#get order of mean posterior
ord<-post %>% filter(variable=="mean") %>% arrange(value) %>% .$Hummingbird

b$Hummingbird<-factor(b$Hummingbird,levels=ord)
ggplot(b,aes(y=estimate,x=Hummingbird,fill=Total_Culmen)) + geom_violin() + coord_flip() + scale_fill_continuous(low='blue',high='red') + ggtitle("Traitmatching and Bill Length") + theme_bw()
```

##Interaction and Bill Length

Do species with long bill lengths have positive interaction effects?

```{r,fig.height=7,fig.width=8}
#species names
b<-pars_detect[pars_detect$par %in% "beta3",]
b<-merge(b,jagsIndexBird,by.x="species",by.y="jBird")

#traits
b<-merge(b,hum.morph,by.x="Hummingbird",by.y="English")

post<-b %>% filter(par %in% "beta3") %>% group_by(Hummingbird) %>% summarize(mean=mean(estimate),median=median(estimate),lower=quantile(probs=0.025,estimate),upper=quantile(probs=0.975,estimate),quantile_l=quantile(estimate)[[1]],quantile_u=quantile(estimate)[[2]]) %>% melt(id.vars='Hummingbird')

#get order of mean posterior
ord<-post %>% filter(variable=="mean") %>% arrange(value) %>% .$Hummingbird

b$Hummingbird<-factor(b$Hummingbird,levels=ord)
ggplot(b,aes(y=estimate,x=Hummingbird,fill=Total_Culmen)) + geom_violin() + coord_flip() + scale_fill_continuous(low='blue',high='red') + ggtitle("Interaction Effect and Bill Length") + theme_bw()

```

#Estimated niche breadth

```{r}
castdf<-dcast(pars_detect[pars_detect$par %in% c("beta1","beta2","beta3","alpha"),], species +Chain + Draw~par,value.var="estimate")

#Turn to 
castdf$species<-factor(castdf$species,levels=1:max(as.numeric(castdf$species)))

species.split<-split(castdf,list(castdf$species),drop = T)

species.traj<-lapply(species.split,function(dat){
  index<-unique(dat$species)
  
  #get data for those species
  billd<-indat[indat$jBird %in% index,]
  
  d<-data.frame(alpha=dat$alpha,beta1=dat$beta1,beta2=dat$beta2,beta3=dat$beta3)
  
  #fit regression for each input estimate
  sampletraj<-list()
  
  for (y in 1:nrow(d)){
    v=exp(d$alpha[y] + d$beta1[y] * billd$Traitmatch + d$beta2[y] * billd$scaledR + d$beta3[y] * billd$Traitmatch*billd$scaledR)
    
    sampletraj[[y]]<-data.frame(x=as.numeric(billd$Traitmatch),y=as.numeric(v),r=as.numeric(billd$scaledR),jBird=billd$jBird,jPlant=billd$jPlant,jTime=billd$jTime)
  }
  
  sample_all<-rbind_all(sampletraj)
})
  
species.traj<-rbind_all(species.traj)
```

Mean Estimates for Corolla Sizes

```{r}
species.mean<-species.traj %>% group_by(jBird,jPlant,r) %>% summarize(Traitmatch=unique(x),lambda=mean(y))

species.mean<-merge(species.mean,indat[,colnames(indat) %in% c("jBird","jPlant","jTime","Hummingbird","Iplant_Double")])

#get corolla sizes
species.mean<-merge(species.mean,fl.morph,by.x="Iplant_Double", by.y="Group.1")

ggplot(species.mean) + geom_density2d(aes(x=TotalCorolla,y=lambda,col=Hummingbird)) + theme_bw() + facet_wrap(~r,scales="free") 
#bill order
ord<-hum.morph %>% arrange(Total_Culmen) %>% .$English
species.mean$Hummingbird<-factor(species.mean$Hummingbird,levels=ord)

#add level to hum.morph to match naming convention
species.mean<-merge(species.mean,hum.morph[,c("English","Total_Culmen")],by.x="Hummingbird",by.y="English")

p<-ggplot(species.mean,aes(x=TotalCorolla,y=lambda,col=as.factor(BUsed_Flowers))) + geom_line(size=.9) + geom_vline(aes(xintercept=Total_Culmen),linetype='dashed') + facet_wrap(~Hummingbird,ncol=3,scales="free_y")  + theme_bw() + ylab("Estimated Daily Interaction Rate") + scale_color_manual("Resource Availability",labels=c("Low","High"),values=c("Blue","Red")) + xlab("Flower Corolla Length (mm)") 
p
ggsave("Figures/ResponseCurves.jpeg",height=6.5,width=9)
```

Density curves

```{r}
ggplot(species.mean) + geom_density2d(aes(x=TotalCorolla,y=lambda,col=as.factor(BUsed_Flowers))) + theme_bw() + facet_wrap(~Hummingbird,scales="free",ncol=3)+ scale_color_manual("Resources Availability",labels=c("Low","High"),values=c("Blue","Red")) + ggtitle("2D Density Plots") + geom_vline(aes(xintercept=Total_Culmen),linetype='dashed')
```

#Niche Breadth 

```{r}
species.mean<-species.traj %>% group_by(jBird,jPlant,r) %>% summarize(Traitmatch=unique(x),lambda=mean(y),lambda_low=quantile(y,0.05),lambda_high=quantile(y,0.95))

species.mean<-merge(species.mean,indat[,colnames(indat) %in% c("jBird","jPlant","jTime","Hummingbird","Iplant_Double"," BUsed_Flowers")])

#get corolla sizes
species.mean<-merge(species.mean,fl.morph,by.x="Iplant_Double", by.y="Group.1")

#bill order
ord<-hum.morph %>% arrange(Total_Culmen) %>% .$English
species.mean$Hummingbird<-factor(species.mean$Hummingbird,levels=ord)

#add level to hum.morph to match naming convention
species.mean<-merge(species.mean,hum.morph[,c("English","Total_Culmen")],by.x="Hummingbird",by.y="English")

ggplot(species.mean) + geom_ribbon(alpha=0.2,aes(x=TotalCorolla,ymin=lambda_low,ymax=lambda_high,fill=as.factor(r))) + theme_bw() + facet_wrap(~Hummingbird,scales="free",ncol=3)+ scale_fill_manual("Resources Availability",labels=c("Low","High"),values=c("Blue","Red")) + ggtitle("Niche Breadth") + geom_vline(aes(xintercept=Total_Culmen),linetype='dashed') + geom_line(aes(x=TotalCorolla,y=lambda,fill=as.factor(r))) + ylab("Estimated Daily Intensity") + xlab("Corolla Length (mm)")
ggsave("Figures/NicheBreadth.jpeg",height=6,width=9)
```

Standardized intensity of niche breadth

```{r}
sm<-split(species.mean,species.mean$Hummingbird,drop=T)
sm<-lapply(sm,function(x){
  x$lambda<-x$lambda/max(x$lambda)
  x$lambda_low<-x$lambda_low/max(x$lambda_low)
  x$lambda_high<-x$lambda_high/max(x$lambda_high)
  return(x)
})
species.max<-rbind_all(sm)

ggplot(species.max,aes(x=TotalCorolla,y=lambda,col=as.factor(BUsed_Flowers))) + geom_density2d() + theme_bw() + scale_color_manual("Resources Availability",labels=c("Low","High"),values=c("Blue","Red")) + scale_y_continuous(breaks=c(0,1),labels=c("Low","High")) + xlab("Flower Corolla Length") + ylab("Hummingbird Visitation")
```

#Generate network
```{r}

```{r}
spdf<-dcast(pars[pars$par %in% c("alpha","beta1","beta2"),], Chain + species+  Draw~par,value.var="estimate")

trait_model<-matrix(nrow=h_species,ncol=plant_species)
colnames(trait_model)<-1:ncol(trait_model)
rownames(trait_model)<-1:nrow(trait_model)

for( x in 1:h_species){
    spdat<-filter(spdf,species==x)
    draw<-spdat[sample(1:nrow(spdat),1),]
    
    #For each plant species create a deviate
    for (y in 1:plant_species){
      prob=inv.logit(draw$alpha + draw$beta1 * traitmatch[x,y])
      trait_model[x,y]<-rbinom(1,1,prob)
    }
}

plotweb(trait_model)
```

```{r}
save.image("ObservedModel.RData")
```
